{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update slides
The slides have been updated including the pdf file from Ken on AUG

\begin{frame}{Fast electron generation}

>>>>

\begin{frame}{Fast electron generation}
\Fontvi
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/SXR_ken}}
    \end{column}
    \begin{column}{0.5\textwidth}
\begin{itemize}
      \item Bursts of nonthermal 2nd harmonic electron cyclotron emission and edge soft X-ray emission often occur at start of ELM filament eruption in low collisionality AUG pulses – evidence of filament reconnection
\item Soft X-ray bursts were seen at start of ELM filament eruption in T21-AUG pulses, but not ECE bursts, probably due to higher collisionality in these pulses
\item Peak nonthermal ECE emission appears to originate from top of pedestal
\item Work is ongoing to determine conditions for occurrence of ECE \& SXR bursts, e.g. in terms of pedestal collisionality – there is no clear correlation between ELM size \& SXR flux
\end{itemize}
\end{column}

  \end{columns}
\end{frame}
